Incorporating individual variation in animal movement models

### 2021-03-15 distributions_paper/format_raw_dat.Rmd
New paper on fitting distributions

---
title: "Incorporating individual variation in animal movement models"
subtitle: "Explore data and sampling sequences"
output:
  html_document:
      toc: true
bibliography: "aracari_movement.bib"
---

@@

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```

@@

```{r data}
# First, read in the raw tracking data
# aracari_data <- read.csv("data/raw_location_data.csv")
aracari_data <- read.csv("movement_paper/rawdata_ptpl.csv")
# Time is presented as a time ID
# Each time interval is equivalent to 15 minutes
# Interval 1 == 6AM, so if we start at midnight, 6am is 24 intervals of 15 minutes each. I'm setting 6am as the start just because I don't have actual data on it, but we know they started early morning and that's what the time IDs are for in Kimberly's work.

@@

## Home range

```{r}
# Use only ones with more than 40 locations

@@

## moveHMM

```{r}
library(moveHMM)

aracari_df %>% 
  dplyr::select(., id, dist, abs.angle) %>% 
  drop_na(dist) %>% 
  rename(ID = id,
         step = dist,
         angle = abs.angle) -> d

fithmm <- fitHMM(d)

# I don't think I can use the package because my data is different. It is not continuous time series, and it doesn't take into account irregular sampling intervals.
```

>>>>

---
title: "Incorporating individual variation in animal movement models"
subtitle: "Explore data and sampling sequences"
output:
  html_document:
      toc: true
bibliography: "aracari_refs.bib"
---

@@

```{r setup, include=FALSE}
# knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```

@@

```{r data}
# First, read in the raw tracking data
# aracari_data <- read.csv("data/raw_location_data.csv")
aracari_data <- read.csv("rawdata_ptpl.csv")
# Time is presented as a time ID
# Each time interval is equivalent to 15 minutes
# Interval 1 == 6AM, so if we start at midnight, 6am is 24 intervals of 15 minutes each. I'm setting 6am as the start just because I don't have actual data on it, but we know they started early morning and that's what the time IDs are for in Kimberly's work.

@@

<!-- ## Home range -->

```{r eval = FALSE}
# Use only ones with more than 40 locations

@@
